Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ \smaller \textbf{{London version \YellowPaperVersionNumber}}

### 2023-11-08 Paper.tex
missing period

There are differences in how one's acceptable gas price is specified in type 2 transactions versus type 0 and type 1 transactions. Type 2 transactions take better advantage of the gas market improvements introduced in EIP-1559 by explicitly limiting the \textit{priority fee}\footnote{The \textit{priority fee} is discussed in greater detail in sections \ref{ch:payment} and \ref{ch:transactions}} that is paid. Type 2 transactions have the following two fields related to gas:

>>>>

There are differences in how one's acceptable gas price is specified in type 2 transactions versus type 0 and type 1 transactions. Type 2 transactions take better advantage of the gas market improvements introduced in EIP-1559 by explicitly limiting the \textit{priority fee}\footnote{The \textit{priority fee} is discussed in greater detail in sections \ref{ch:payment} and \ref{ch:transactions}.} that is paid. Type 2 transactions have the following two fields related to gas:
